\section*{Experience}

\textbf{Rocket Software} \hfill Vilnius, Lithuania \\
\textit{Principal Software Engineer} \hfill Mar 2025 -- Present

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Lead architecture and technical direction for performance-critical monitoring and diagnostic components in IBM z/OS and hybrid environments.
  \item Act as a technical authority across teams, unblocking complex issues involving dumps, diagnostics, protocols, and legacy codebases.
  \item Mentor engineers and drive cross-team collaboration, raising system-level expertise and delivering reliable, scalable solutions.
\end{itemize}

\textit{Senior Software Engineer} \hfill Apr 2023 -- Mar 2025

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Led modernization of legacy mainframe tooling, introducing RESTful interfaces while preserving performance and reliability guarantees.
  \item Contributed to architectural decisions and implementation of system-level components in C/C++ and Java within mainframe monitoring systems.
  \item Actively supported less experienced engineers through code reviews, design discussions, and debugging of complex issues.
\end{itemize}

\textit{Software Engineer III / II} \hfill Dec 2020 -- Apr 2023

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Developed performance-sensitive C/C++ and HLASM components for the OMEGAMON monitoring suite on IBM z/OS.
  \item Worked extensively with system dumps, protocol handling, and low-level diagnostic tooling.
  \item Improved delivery reliability through CI/CD contributions.
\end{itemize}

\textbf{Sonderus} \hfill Vilnius, Lithuania \\
\textit{Software Developer} \hfill Jul 2019 -- Dec 2020

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Developed embedded C/C++ software and Linux kernel modules for system-level tools.
\end{itemize}

\textbf{Precizika Metrology} \hfill Vilnius, Lithuania \\
\textit{Engineer Programmer} \hfill Oct 2017 -- Jul 2019

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Designed firmware and calibration systems for precision linear encoders.
  \item Developed signal processing tools and supporting PCBs for nanometer-level measurement accuracy.
\end{itemize}

\textbf{Vilnius Gediminas Technical University} \hfill Vilnius, Lithuania \\
\textit{Junior Researcher} \hfill Nov 2016 -- Aug 2017

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Supported biomechanics research projects using MATLAB and signal analysis.
\end{itemize}

\textbf{Various Roles (Freelance, Part-time)} \hfill Kharkiv, Ukraine \\
\textit{System Admin / Electrician / Developer} \hfill 2008 -- 2016

\vspace{-0.5em}
\begin{itemize}[leftmargin=*]
  \item Early technical roles in system administration, hardware support, and embedded integration, building a strong foundation in operating systems and networking.
\end{itemize}